Brandt et al. example: equivalent & not significant

### 2017-10-19 NSEQ_Brandt_Example.Rmd

# replication study: Brandt et al., study 1
rep.m1 <- 4.79
rep.m2 <- 4.66
rep.sd1 <- 1.09
rep.sd2 <- 1.19
rep.n1 <- 49
rep.n2 <- 51
rep.t <- 0.56
rep.p <- .574
rep.df <- rep.n1 + rep.n2 - 2
rep.d <- 0.11

>>>>

# replication study: Brandt et al., study 1
rep.m1 <- 4.7857
rep.m2 <- 4.6569
rep.sd1 <- 1.0897
rep.sd2 <- 1.1895
rep.n1 <- 49
rep.n2 <- 51
rep.t <- 0.56
rep.p <- .574
rep.df <- rep.n1 + rep.n2 - 2
rep.d <- 0.11
